The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging with the Owens Valley Long Wavelength Array

### 2017-04-03 paper.tex
explain how Tikhonov regularization improves the noise properties

\renewcommand{\b}{\pmb}
\renewcommand{\d}{{\rm d}}
\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1!}}

@@

Another way of looking at the problem is that because the interferometer is not sensitive to part of
the southern hemisphere, there are infinitely many possible solutions to
equation~\ref{eq:m-mode-matrix-equation} that will fit the measured data equally well. So we need to
regularize the problem and apply an additional constraint that prefers a unique solution. For
example, you may prefer that in the absence of any information the sky should be set to zero or you
may prefer that the sky should be set to some prior expectation. The process of Tikhonov
regularization minimizes $\|\b v - \b B\b a\|^2 + \epsilon\|\b a\|^2$ for some arbitrary value of
$\epsilon > 0$ chosen by the observer. The solution that minimizes this expression is given by
\begin{equation}
    \b{\hat a}_\text{Tikhonov} = (\b B^*\b B + \epsilon\b I)^{-1}\b B^*\b v\,.
\end{equation}
Tikhonov regularization adds a small value $\epsilon$ to the diagonal of $\b B^*\b B$, fixing the
matrix's singularity.

\todo{describe how Tikhonov regularization improves the noise properties of the map}

>>>>

\renewcommand{\b}{\pmb}
\renewcommand{\d}{{\rm d}}
\newcommand{\atikh}{\b{\hat a}_\text{Tikhonov}}
\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1!}}

@@

Another way of looking at the problem is that because the interferometer is not sensitive to part of
the southern hemisphere, there are infinitely many possible solutions to
equation~\ref{eq:m-mode-matrix-equation} that will fit the measured data equally well. So we need to
regularize the problem and apply an additional constraint that prefers a unique solution. For
example, you may prefer that in the absence of any information the sky should be set to zero or you
may prefer that the sky should be set to some prior expectation.

The process of Tikhonov regularization minimizes $\|\b v - \b B\b a\|^2 + \epsilon\|\b a\|^2$ for
some arbitrary value of $\epsilon > 0$ chosen by the observer. The solution that minimizes this
expression is given by
\begin{equation}\label{eq:tikhonov-solution}
    \atikh = (\b B^*\b B + \epsilon\b I)^{-1}\b B^*\b v\,.
\end{equation}
Tikhonov regularization adds a small value $\epsilon$ to the diagonal of $\b B^*\b B$, fixing the
matrix's singularity. We can see this by using the singular value decomposition (SVD) of the matrix
$\b B = \b U \b \Sigma \b V^*$. Equation~\ref{eq:tikhonov-solution} becomes
\[
    \atikh = \b V (\b\Sigma^2 + \epsilon \b I)^{-1}\b\Sigma \b U^*\b v\,.
\]
The diagonal elements of $\b\Sigma$ are the singular values of $\b B$ and so the contribution of
each singular component to the Tikhonov-regularized solution is scaled by $\sigma / (\sigma^2 +
\epsilon)$, where $\sigma$ is the singular value for the given singular component. Tikhonov
regularization therefore acts to suppress any component for which $\sigma\lesssim\sqrt{\epsilon}$.
If $\sigma = 0$, the component is set to zero.

In practice the measurement $\b v$ is corrupted by noise with covariance $\b N$. For illustrative
purposes we now assume that $\b N=n\b I$ for some scalar $n$. In this case the covariance of the
Tikhonov-regularized spherical harmonic coefficients $\b C = \left\langle\atikh^*\atikh\right\rangle
- \left\langle\atikh\right\rangle\left\langle\atikh^*\right\rangle$ is
\begin{equation}
    \b C = n \b V \b\Sigma^2 (\b\Sigma^2 + \epsilon\b I)^{-2} \b V^*\,.
\end{equation}
Each singular component is scaled by a factor of $\sigma^2/(\sigma^2 + \epsilon)^2$.
In the absence of Tikhonov regularization ($\epsilon=0$)
singular components with the smallest singular values -- the ones that the interferometer is
the least sensitive to -- actually come to dominate the covariance of the measured spherical
harmonic coefficients. Tikhonov regularization improves this situation by downweighting these
components.
